---
title: "REMIND-PyPSA Validation"
author: "Adrian Odenweller"
date: "2023-03-04"
output:
  pdf_document:
    number_sections: true
    fig_width: 10
    fig_height: 6
    extra_dependencies: ["float"]
fontsize: 11pt
geometry: margin=0.5in
---

This RMarkdown file creates a HTML/PDF with several figures for the iterative
REMIND-PyPSA coupling. It relies on the plotting functions in "R/plot<var>.R".

This file can be executed between iterations to analyse convergence progress and
needs to be called from the REMIND output directory, where the results are. 

Additionally, all plots are saved into a "REMIND-PyPSA_Plots" folder (ToDo).

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")

# Color mapping
colorsTech <- c("solar" = "#ffcc00",
                "onwind" = "#337fff",
                "all_offwind" = "#334cff",
                "offwind" = "#334cff",
                "biomass" = "#005900",
                "ror" = "#191999",
                "CCGT" = "#999959",
                "OCGT" = "#e5e5b2",
                "oil" = "#663a00",
                "all_coal" = "#0c0c0c",
                "coal" = "#0c0c0c",
                "lignite" = "#392306",
                "nuclear" = "#ff33ff")

# Pretty name mapping
namesTech <- c("solar" = "Solar",
               "onwind" = "Wind Onshore",
               "all_offwind" = "Wind Offshore",
               "offwind" = "Wind Offshore",
               "biomass" = "Biomass",
               "ror" = "Run of river",
               "CCGT" = "CCGT",
               "OCGT" = "OCGT",
               "oil" = "Oil",
               "all_coal" = "Coal+Lignite",
               "coal" = "Coal",
               "lignite" = "Lignite",
               "nuclear" = "Nuclear")

rm2pyTech <- c(
  "biochp" = "biomass",
  "bioigcc" = "biomass",
  "bioigccc" = "biomass",
  "ngcc" = "CCGT",
  "ngccc" = "CCGT",
  "gaschp" = "CCGT",
  "igcc" = "all_coal",
  "igccc" = "all_coal",
  "pc" = "all_coal",
  "coalchp" = "all_coal",
  "tnrs" = "nuclear",
  "fnrs" = "nuclear",
  "ngt" =  "OCGT",
  "windoff" = "all_offwind",  # Or just offwind?
  "dot" = "oil",
  "wind" = "onwind",
  "hydro" = "ror",
  "spv" = "solar")

py2rmTech <- c(
  "biomass" = "biomass",
  "CCGT" = "CCGT",
  "coal" = "all_coal",  # Aggregate coal
  "lignite" = "all_coal",  # Aggregate coal
  "nuclear" = "nuclear",
  "OCGT" = "OCGT",
  "offwind-ac" = "all_offwind",  # Aggregate offshore wind
  "offwind-dc" = "all_offwind",  # Aggregate offshore wind
  "oil" = "oil",
  "onwind" = "onwind",
  "ror" = "ror",
  "solar" = "solar"
)

years <- c(seq(2025, 2060, 5), seq(2070, 2110, 10), 2130, 2150)
```

# Import data and cross-check

```{r files, echo=FALSE}
# Set results directory
resDir <- getwd()  # REMIND output directory
pyResDir <- file.path(resDir, "pypsa")  # PyPSA output directory
# Get REMIND fulldata files
rmFiles <- list.files(resDir, pattern = "fulldata\\_\\d{1,}.gdx", full.names = TRUE)
# Get REMIND2PyPSA file
remind2pypsa <- readRDS(file.path(resDir, "remind2pypsa.rds"))
# Get PyPSA directories
pyDirs <- list.dirs(path = pyResDir, recursive = FALSE, full.names = TRUE)
# Get PyPSA2REMIND file
pypsa2remind <- readRDS(file.path(resDir, "pypsa2remind.rds"))

# REMIND fulldata files
cat(paste("Found", length(rmFiles), "REMIND fulldata gdx files.\n"))
# REMIND2PyPSA file
cat(paste("Found REMIND to PyPSA file with",
            length(unique(remind2pypsa$variable)), "different variable(s):",
            toString(unique(remind2pypsa$variable)), "\n"))
# Cross-check number of PyPSA result directories
for (y in years){
  pyDirIters <- pyDirs[grepl(y, pyDirs)] %>%
    stringr::str_extract("(?<=i)\\d{1,}") %>%
    unique() %>%
    as.integer() %>%
    sort()
  if (length(pyDirIters) != length(rmFiles)) {
    warning("Number of PyPSA result directories inconsistent with REMIND in year ", y, "\n")
  }
}
# PyPSA directories
cat(paste("Found", length(pyDirs), "PyPSA directories for", length(years),
          "time steps with", length(pyDirIters), "iterations each.\n"))
# PyPSA2REMIND file
cat(paste("Found PyPSA to REMIND file with",
            length(unique(pypsa2remind$var)), "different variable(s):",
            toString(unique(pypsa2remind$var))))
```

# Coupled variables

This section includes plots of all variables that are exchanged between REMIND
and PyPSA.

## REMIND to PyPSA

### Electricity load

### Pre-investment capacities

### Capital costs and marginal costs

```{r}
costs <- remindPypsa::plotCosts(remind2pypsa, colorsTech, namesTech)

for (p in costs) print(p)
```



## PyPSA to REMIND

### Capacity factors

REMIND values are calculated from fulldata_*.gdx to cross-check.
PyPSA values come from pypsa2remind.rds.

```{r capfac, echo = FALSE, message = FALSE}
capfac <- remindPypsa::plotCapfac(resDir, years, rm2pyTech, colorsTech, namesTech)

for (p in capfac) print(p)
```


### Market values

### Capacity constraint

# Non-coupled variables

This section includes plots of several key variables that are not coupled
between REMIND and PyPSA, but that should get harmonised

## Capacity

## Generation

## Electricity price

# Model-specific variables

## REMIND

## PyPSA

### Screening curve

### Inverse screening curve

### Residual Load Duration Curve

